### 2024-07-19 doc/example.tex
Update README.md and examples
Update examples

\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}

LitREPL treats \texttt{lcode} environment as code sections and \texttt{lresult}
environment as result sections. The names are currently hardcoded into the
simplified LitREPL parser. Wrapping it in other tags is not allowed.

LaTeX does not know anything about these environments by default, we need to
introduce them to be able to compile the document using e.g. \texttt{pdflatex}.

\newenvironment{lcode}{\begin{texttt}}{\end{texttt}}
\newenvironment{lresult}{\begin{texttt}}{\end{texttt}}
\newcommand{\linline}[2]{#2}

Executable section is the text between the \texttt{lcode} begin/end tags.

\begin{lcode}
W='Hello, World!'
print(W)
\end{lcode}

Putting the cursor on it and typing the \texttt{:LitEval1} runs the code in the
background Python interpreter.

\texttt{lresult} begin/end tags mark the result section.  LitREPL replaces its
content with the above code section's execution result.

\begin{lresult}
Hello, World!
\end{lresult}

LitREPL recognizes \texttt{l[no]code}/\texttt{l[no]result} comments as
code/result section markers. This way we can use Python to produce LaTeX markup
as output.

%lcode
print("Hi!")
%lnocode

%lresult
Hi!
%lnoresult

Additionally, VimREPL recognises \texttt{linline} 2-argument tags. The first
arguement is treaten as a Python printable expression. The second arguemnt is to
be replaced with the printing output. In our simplified definition, we simply
ignore the first argument and paste the second to the LaTeX processor as-is.

\linline{W}{Hello, World!}

>>>>

\documentclass{article}
\usepackage{verbatim}
\usepackage{mdframed}
\usepackage{minted}
\renewcommand{\MintedPygmentize}{pygmentize}
\usepackage[utf8]{inputenc}

% LitREPL-compatible environment for code snippets
\newenvironment{python}
  {\VerbatimEnvironment
   \begin{minted}[breaklines,fontsize=\footnotesize]{python}}
  {\end{minted}}
\BeforeBeginEnvironment{python}{
  \begin{mdframed}[nobreak=true,frametitle=\tiny{Python}]}
\AfterEndEnvironment{python}{\end{mdframed}}

% LitREPL-compatible environment for code results
\newenvironment{result}{\verbatim}{\endverbatim}
\BeforeBeginEnvironment{result}{
  \begin{mdframed}[frametitle=\tiny{Result}]\footnotesize}
\AfterEndEnvironment{result}{\end{mdframed}}

% LitREPL-compatible command for inline code results
\newcommand{\linline}[2]{#2}

\begin{document}

\section{Preamble}

Litrepl uses its own internal parser to determine LaTeX-looking tags defining
code and result sections. As one option, it expects \texttt{python} environment
to mark code and \texttt{result} wrapping results. Both tags need to be
introduced to LaTeX so it doesn't get confused. The following preamble sets both
environments to be rendered as framed boxes of fixed-width text with proper
highlighting:

\begin{verbatim}
\newenvironment{python}
  {\VerbatimEnvironment
   \begin{minted}[breaklines,fontsize=\footnotesize]{python}}
  {\end{minted}}
\BeforeBeginEnvironment{python}{
  \begin{mdframed}[nobreak=true,frametitle=\tiny{Python}]}
\AfterEndEnvironment{python}{\end{mdframed}}

\newenvironment{result}{\verbatim}{\endverbatim}
\BeforeBeginEnvironment{result}{
  \begin{mdframed}[frametitle=\tiny{Result}]\footnotesize}
\AfterEndEnvironment{result}{\end{mdframed}}
\end{verbatim}

\section{Basic evaluation}

\begin{verbatim}
\begin{python}
W='Hello, World!'
print(W)
\end{python}
\end{verbatim}

\begin{python}
W='Hello, World!'
print(W)
\end{python}

Putting the cursor on it and typing the \texttt{:LEval} runs the code in the
background Python interpreter.

\texttt{result} begin/end tags mark the result section.  LitREPL replaces its
content with the above code section's execution result.

\begin{verbatim}
\begin{result}
Hello, World!
\end{result}
\end{verbatim}

\begin{result}
Hello, World!
\end{result}

\section{Producing LaTeX}

LitREPL also recognizes \texttt{result}/\texttt{noresult} comments as result
section markers. With their help we can directly produce LaTeX markup as output:

\begin{verbatim}
\begin{python}
print("\\textbf{Hi!}")
\end{python}

%result
\textbf{Hi!}
%noresult
\end{verbatim}

\begin{python}
print("\\textbf{Hi!}")
\end{python}

%result
\textbf{Hi!}
%noresult

\section{Inline output}

Additionally, VimREPL recognises \texttt{linline} 2-argument tags. The first
arguement is treaten as a Python printable expression. The second arguemnt is to
be replaced with its value.

The value of \texttt{W} is happen to be: \linline{W}{Hello, World!}
